---
title: "CovidVaccineSites"
author: "Drew Walker"
date: "2/6/2021"
output: html_document
---

```{r setup, include=FALSE}
library(jsonlite); packageVersion("jsonlite")
library(knitr); packageVersion("knitr")
library(purrr); packageVersion("purrr")
library(polite); packageVersion("polite")
library(aws.alexa); packageVersion("aws.alexa")
library(RCurl); packageVersion("RCurl")
library(tidyverse); packageVersion("tidyverse")
library(stringr); packageVersion("stringr")
library(rvest); packageVersion("rvest")
library(sp)
library(maps)
library(maptools)
```

# Load Data on GA Vaccine Locations

-   [\<https://opendata.atlantaregional.com/datasets/JohnsCreekGA::vaccination-locations-in-georgia/data?geometry=-87.910%2C29.898%2C-78.813%2C36.333\>](https://nam11.safelinks.protection.outlook.com/?url=https%3A%2F%2Fopendata.atlantaregional.com%2Fdatasets%2FJohnsCreekGA%3A%3Avaccination-locations-in-georgia%2Fdata%3Fgeometry%3D-87.910%252C29.898%252C-78.813%252C36.333&data=04%7C01%7Candrew.walker%40emory.edu%7Cfb5e2f80f2ae44ab8cab08d8cb19d112%7Ce004fb9cb0a4424fbcd0322606d5df38%7C0%7C0%7C637482659032160171%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C1000&sdata=3scGweksr%2BqLzj%2FBt%2BQXhe3N8fqY1M5ik9%2B%2BFO622YM%3D&reserved=0 "Original URL: https://opendata.atlantaregional.com/datasets/JohnsCreekGA::vaccination-locations-in-georgia/data?geometry=-87.910%2C29.898%2C-78.813%2C36.333. Click or tap if you trust this link.")

-   

```{r, get_data}

locations <- jsonlite::fromJSON("https://opendata.arcgis.com/datasets/123f98093dd249159bdb635f4b834fc0_0.geojson", flatten = TRUE)

location_list <- locations$features

kable(location_list)
```

# Get site traffic estimations for each site's page on ga public health website

<https://github.com/cloudyr/aws.alexa>

```{r scrape-clinic-site-function}
library(rvest)

get_clinic_site_traffic <- function(ga_dph_url){
site_webpage <- read_html(ga_dph_url) %>% 
  html_nodes(".contact__link a") %>% 
  html_attrs() %>% 
  unlist() %>% 
  str_remove("href") 
traffic <- traffic_history(site_webpage)
return(traffic)
}

```

```{r, alexa-get-data}

creds_raw <- read_csv("rootkey.csv", col_names = FALSE)
creds <- sub("^[^_]*=", "", creds_raw)

test <- head(location_list, n = 20)
test <- location_list



creds_ready <- creds_raw %>% 
  mutate(correct = substring(X1, regexpr("=", X1) + 1, nchar(X1))) %>% 
  select(correct)
set_secret_key(key = creds_ready[1,1], secret = creds_ready[2,1])

test_real_url <- traffic_history("https://www.yourtownhealth.com/")


test_gph_url <- traffic_history("https://dph.georgia.gov/locations/clayton-county-health-department-forest-park-rec-covid-vaccine")
library(purrr)
library(furrr)
possible_nonsite <- purrr::possibly(get_clinic_site_traffic, otherwise = tidyr::tibble("NA"))
test_webdata <- test %>% 
  mutate(web_history = future_map(test$properties.AdditionalData, possible_nonsite),
         ga_dph_history = future_map(test$properties.AdditionalData,traffic_history)) 


```

```{r read-data}

#OR read in file

web_data_file_list <- list.files(pattern="* clinic_web_traffic_data.rds")

test_webdata <- lapply(web_data_file_list, readRDS)


test_webdata <- test_webdata[[1]]

test_webdata$ga_dph_history
#Tidy Version
clinic_web_traffic_data <- test_webdata %>%
  unnest(web_history) 

clinic_web_traffic_data_to_merge <- clinic_web_traffic_data %>% 
  select(date,
         properties.OBJECTID,
         site,
         start,
         range,
         page_views_per_million,
         page_views_per_user,
         rank,
         reach_per_million)
colnames(clinic_web_traffic_data_to_merge) <- paste("clinic_site", colnames(clinic_web_traffic_data_to_merge), sep = "_")

clinic_web_traffic_data_to_merge <- clinic_web_traffic_data_to_merge %>% 
  rename(properties.OBJECTID = clinic_site_properties.OBJECTID,
         date=clinic_site_date)

ga_dph_site_traffic_data <- test_webdata %>% 
  unnest(ga_dph_history)
colnames(ga_dph_site_traffic_data) <- paste("ga_dph_site", colnames(ga_dph_site_traffic_data), sep = "_")

ga_dph_site_traffic_data_to_merge <- ga_dph_site_traffic_data %>% 
  rename(properties.OBJECTID = ga_dph_site_properties.OBJECTID,
         date=ga_dph_site_date)


merged_dataset <- left_join(ga_dph_site_traffic_data_to_merge,clinic_web_traffic_data_to_merge, by = c("properties.OBJECTID","date"))
```


# Need to bring in county variable 

```{r getting-counties}
library(sp)
library(maps)
library(maptools)

# The single argument to this function, pointsDF, is a data.frame in which:
#   - column 1 contains the longitude in degrees (negative in the US)
#   - column 2 contains the latitude in degrees

mapping_split <- merged_dataset %>% 
  unnest_wider(ga_dph_site_geometry.coordinates)


lonlat <- tibble(mapping_split$...1, mapping_split$...2)
lonlat <- as.data.frame(lonlat)


lonlat_to_state_sp <- function(pointsDF) {
    # Prepare SpatialPolygons object with one SpatialPolygon
    # per state (plus DC, minus HI & AK)
    states <- map('county', fill=TRUE, col="transparent", plot=FALSE)
    IDs <- sapply(strsplit(states$names, ":"), function(x) x[1])
    states_sp <- map2SpatialPolygons(states, IDs=IDs,
                     proj4string=CRS("+proj=longlat +datum=WGS84"))

    # Convert pointsDF to a SpatialPoints object 
    pointsSP <- SpatialPoints(pointsDF, 
                    proj4string=CRS("+proj=longlat +datum=WGS84"))

    # Use 'over' to get _indices_ of the Polygons object containing each point 
        indices <- over(pointsSP, states_sp)

    # Return the state names of the Polygons object containing each point
    stateNames <- sapply(states_sp@polygons, function(x) x@ID)
    stateNames[indices]
}
lonlat_with_counties <- lonlat %>% 
  mutate(county_raw = lonlat_to_state_sp(lonlat))
counties <- lonlat_to_state_sp(lonlat)

mapping_split_counties <- mapping_split %>% 
  mutate(county_raw = lonlat_to_state_sp(tibble(...1,...2)),
         county_clean = str_to_title(str_extract(county_raw, "(?<=georgia,)\\w+")))

mapping_split_counties_and_fips <- left_join(mapping_split_counties,county.fips, by = c("county_raw"="polyname"))

county.fips
                                                                   
```


# COVID-19 GA County Data

```{r, GACOVIDcsv}
temp <- tempfile()
download.file("https://ga-covid19.ondemand.sas.com/docs/ga_covid_data.zip",temp)
ga_county_covid_data <- read_csv(unz(temp, "county_cases.csv")) %>% 
  mutate(date = Sys.Date())
unlink(temp)

download.file("https://ga-covid19.ondemand.sas.com/docs/ga_covid_data.zip",temp)
ga_county_covid_data_demographics_race <- read_csv(unz(temp, "demographics_by_race_eth.csv"))%>% 
  mutate(date = Sys.Date())
unlink(temp)

download.file("https://ga-covid19.ondemand.sas.com/docs/ga_covid_data.zip",temp)
ga_county_covid_data_demographics_race <- read_csv(unz(temp, "demographics_by_race_eth.csv"))%>% 
  mutate(date = Sys.Date())
unlink(temp)

download.file("https://ga-covid19.ondemand.sas.com/docs/ga_covid_data.zip",temp)
ga_county_covid_data_demographics_sex <- read_csv(unz(temp, "demographics_by_sex.csv")) %>% 
  mutate(date = Sys.Date())
unlink(temp)

download.file("https://ga-covid19.ondemand.sas.com/docs/ga_covid_data.zip",temp)
ga_county_covid_data_demographics_age <- read_csv(unz(temp, "demographics_by_age_group.csv")) %>% 
  mutate(date = Sys.Date())
unlink(temp)
```

```{r, write_dataframes}
clinic_web_traffic_data_tibble <- as_tibble(test_webdata)

clinic_web_traffic_data_filename <- paste(Sys.Date(),"clinic_web_traffic_data.rds")

ga_county_covid_data_filename <- paste(Sys.Date(),"ga_county_covid_data.rds")

ga_county_covid_data_demographics_race_filename <- paste(Sys.Date(),"ga_county_covid_data_demographics_race.rds")

ga_county_covid_data_demographics_sex_filename <- paste(Sys.Date(),"ga_county_covid_data_demographics_sex.rds")

ga_county_covid_data_demographics_age_filename <- paste(Sys.Date(),"ga_county_covid_data_demographics_age.rds")

mapping_split_counties_and_fips_filename <- paste(Sys.Date(),"mapping_split_counties_and_fips.rds")


saveRDS(test_webdata, clinic_web_traffic_data_filename)
saveRDS(ga_county_covid_data, ga_county_covid_data_filename)
saveRDS(ga_county_covid_data_demographics_race, ga_county_covid_data_demographics_race_filename)
saveRDS(ga_county_covid_data_demographics_sex, ga_county_covid_data_demographics_sex_filename)
saveRDS(ga_county_covid_data_demographics_age, ga_county_covid_data_demographics_age_filename)

saveRDS(mapping_split_counties_and_fips,mapping_split_counties_and_fips_filename)

```

# COVID Vaccine Rate for Georgia

-   <https://datastudio.google.com/u/0/reporting/d848d61a-e99e-4961-b040-02b43edc5bb5/page/ptmtB>

-   How to get data pulls from this graphic?

-   

    # Google Trends Data r package

-   <https://cran.r-project.org/web/packages/gtrendsR/gtrendsR.pdf>

# Webscraping COVID Vaccine Distribution

<https://covid.cdc.gov/covid-data-tracker/#vaccinations>

-   There is a download .csv button here, that gives a dated/timestamped set of information on state-by-state vaccine allocation and administration dates.

# GA Vaccine Allocations PDF by clinic site/County

For this we use a pdf webscraping R code for the GA DPH vaccine order list pdf developed by Brad Brewington! <https://github.com/bbrewington>

-   <https://dph.georgia.gov/document/document/georgia-covid-19-vaccine-plan/download>

-   PDF- may be difficult to scrape GA DPH vaccine order list pdf thanks to <https://github.com/bbrewington> !

# GA DPH Vaccine Distribution Dashboard

<https://experience.arcgis.com/experience/3d8eea39f5c1443db1743a4cb8948a9c/>

```{r, try-with-rvest }
url <- "https://experience.arcgis.com/experience/3d8eea39f5c1443db1743a4cb8948a9c/"
css_selector <- "#g"
tables <- read_html(url) %>% 
  rvest::html_nodes(css_selector)

attrs <- html_attrs(tables)
tables$node



```

```{r selenium}
library(RSelenium)
library(wdman)

library(RSelenium)
driver <- remoteDriver()
driver$open()
driver$navigate("https://www.google.com/")
selServ$process

```

```{r css-code}
<g class="amcharts-graph-column amcharts-graph-graphAuto0_1614382946437" transform="translate(637,386)" aria-label=" Feb 17, 2021 60,297"><path cs="100,100" d="M0.5,0.5 L0.5,-331.5 L8.5,-331.5 L8.5,0.5 L0.5,0.5 Z" fill="#33a3ff" stroke="#33a3ff" fill-opacity="1" stroke-width="1" stroke-opacity="1" class="amcharts-graph-column-front amcharts-graph-column-element"></path></g>
  
  <g class="amcharts-graph-column amcharts-graph-graphAuto0_1614382946437" transform="translate(637,386)" aria-label=" Feb 17, 2021 60,297"><path cs="100,100" d="M0.5,0.5 L0.5,-331.5 L8.5,-331.5 L8.5,0.5 L0.5,0.5 Z" fill="#33a3ff" stroke="#33a3ff" fill-opacity="1" stroke-width="1" stroke-opacity="1" class="amcharts-graph-column-front amcharts-graph-column-element"></path></g>

  
//*[@id="ember154"]/div/div/svg/g[7]/g/g/g[68]


tables$doc

%>% 
  html_nodes("externalptr") %>%
    html_text()
  
  
  
  html_attr()
   html_table(fill = TRUE)

tables <- url  %>%
html_text()

  html_node("xml_node")

  rvest::html_nodes("g")
    
    "g.amcharts-graph-column amcharts-graph-graphAuto0_1614229644565")

<g class="amcharts-graph-column amcharts-graph-graphAuto0_1614229644565" transform="translate(726,386)" aria-label=" Feb 23, 2021 149"><path cs="100,100" d="M0.5,0.5 L0.5,-114.5 L11.5,-114.5 L11.5,0.5 L0.5,0.5 Z" fill="#33a3ff" stroke="#33a3ff" fill-opacity="1" stroke-width="1" stroke-opacity="1" class="amcharts-graph-column-front amcharts-graph-column-element"></path></g>
  %>% 
  purrr::pluck(span)

  html_nodes()

//*[(@id = "ifrSafe")]

  html_nodes("table")
Bowie_songs <- tables %>%
  purrr::pluck(3)%>%
  html_table(fill = TRUE)

#URL for Clinc Site 
url2 <- "https://dph.georgia.gov/locations/1st-care-management"

library(rvest)

get_clinic_site_traffic <- function(ga_dph_url){
site_webpage <- read_html(ga_dph_url) %>% 
  html_nodes(".contact__link a") %>% 
  html_attrs() %>% 
  unlist() %>% 
  str_remove("href") 
traffic <- traffic_history(site_webpage)
return(traffic)
}

traffic_test2 <- get_clinic_site_traffic(url2)



str(site_webpage)
site_webpage$


site_webpage
.contact__link a


#Code for Element 
<a href="https://1stcaremanagement.com/">COVID-19 Vaccine Appointments</a>
#outer-html 
  
  <div class="contact__link"><a href="https://1stcaremanagement.com/">COVID-19 Vaccine Appointments</a></div>
  
  <a href="https://1stcaremanagement.com/">COVID-19 Vaccine Appointments</a>
  
  
```

### How to webscrape in python

<https://towardsdatascience.com/how-to-scrape-a-dashboard-with-python-8b088f6cecf3>

click on County object

\<span style id="ember280"

class="flex-horizontal feature-list-item ember-view"\>

Total vaccines administered that day

\<g class="responsive-text-label"\>

For barchart for county element

\<g class="amcharts-graph-column amcharts-graph-graphAuto0_1614139615882" transform="translate(559,329)" aria-label=" Feb 18, 2021 53,021"\>\<path cs="100,100" d="M0.5,0.5 L0.5,-290.5 L7.5,-290.5 L7.5,0.5 L0.5,0.5 Z" fill="\#33a3ff" stroke="\#33a3ff" fill-opacity="1" stroke-width="1" stroke-opacity="1" class="amcharts-graph-column-front amcharts-graph-column-element"\>\</path\>\</g\>
